\Large \bf Uncovering Bugs in Distributed Storage Systems\\during Testing (not in Production!)

### 2015-09-21 evaluation.tex

The QueryStreamedBackUpNewStream bug in MigratingTable, that was found using \psharp, stands out because it reflects the type of oversight that tends to occur as designs evolve. We do not discuss the details of the bug due to space constraints, but \psharp managed to discover this bug in a matter of seconds. The MigratingTable developers spent just 10 minutes analyzing the trace to diagnose what was happening; although, this was after days of experience analyzing traces. The developers extended the logging of \psharp with additional trace information to understand the bug. \psharp only outputs trace information related to its communicating state machines, but the trace information is easy to extend and was done in all our case studies.

>>>>

The QueryStreamedBackUpNewStream bug in MigratingTable, that was found using \psharp, stands out because it reflects the type of oversight that tends to occur as designs evolve. This bug is in the implementation of a \emph{streaming read} from the virtual table, which should return a stream of all rows in the table sorted by key. The essential implementation idea is to perform streaming reads from both backend tables and merge the results. According to the \texttt{IChainTable} specification, each row read from a stream may reflect the state of the table at any time between when the stream was started and the row was read. The developers sketched a proof that the merging process would preserve this property as long as the migrator was only copying rows from the old table to the new table. But when support was added for the migrator to delete the rows from the old table after copying, it became possible for the backend streams to see the deletion of a row from the old table but not its insertion into the new table, even though the insertion happens first, and the row would be missed. \psharp managed to discover this bug in a matter of seconds. The MigratingTable developers spent just 10 minutes analyzing the trace to diagnose what was happening; although, this was after days of experience analyzing traces and after they had extended the logging of \psharp with additional trace information specific to MigratingTable. \psharp only outputs trace information related to its communicating state machines, but the trace information is easy to extend and was done in all our case studies.
